Follow-up Samples

### 2016-12-07 submission/manuscript_outline_20161024.Rmd
update code  for pvalues and methods section

>>>>

***Investigation of Important CRC Bacteria***
In order to investigate how specific bacteria that have been previously associated with CRC with selected OTUs that taxonomically classified to Fusobacterium Nucleatum, Parvimonas Micra, Peptostreptococcus Assacharolytica, and Porphyromonas Stomatis.  Specifically we wanted to observe if there were any differences based on whether the individual had an adenoma or carcinoma that may have been missed with our lesion versus normal model.
